National Longitudinal Evidence for Growth in Subjective Well-being from Spiritual Beliefs

### 2020-11-30 Supplement_And_Analysis.Rmd
near to final supplement. needs to be proofed

@@

```{r mixing_pwi, cache=TRUE}
plot(mod.1_b, pars ="b_") 
```

```{r mixing_ls, cache=TRUE}
plot(mod.2_b, pars ="b_") 
```

```{r mixing_sd_pwi, cache=TRUE}
plot(mod.1_b, pars ="sd_") #
```

```{r mixing_ls_pwi, cache=TRUE}
plot(mod.2_b, pars ="sd_") # 
```

@@

### ELSE
For the record, we report the fully saturated "everything but the kitchen sink" model.  We show that throwing all regression coefficients produces a stronger effect for beliefs.

```{r lmer model centering years_SATURATED}
library(lme4)
pwi_formulaC <- 'PWI ~  yearsC * Beliefs +  Age_in_Decades_C + Deprivation_S + Education_S  + Employed + Ethnic_Categories + Male  + Has_Partner  + Political_Conservativism_S + Urban + (1+ yearsC|Id)'

ls_formulaC <- 'LIFESAT ~  yearsC * Beliefs +  Age_in_Decades_C + Deprivation_S + Education_S  + Employed + Ethnic_Categories + Male  + Has_Partner  + Political_Conservativism_S + Urban + (1+ yearsC|Id)'
summary(mod.1a)
mod.1a <-lmer (pwi_formulaC, data= d_3)
mod.2a <-lmer (ls_formulaC, data= d_3)

# identical result
performance::check_collinearity(mod.1a)
performance::check_collinearity(mod.2a)
```

Here's the table, again, we find inference is robust.

```{r table of saturated models, cached = TRUE}
sjPlot::tab_model(mod.1a,mod.2a)
```

@@

```{r robust to years and beliefs only, cache = TRUE, dependson=d_3,cache =TRUE}
library(lme4)
pwi_formula_simple <- 'PWI ~  yearsC * Beliefs + (1+ yearsC|Id)'
ls_formula_simple <- 'LIFESAT ~  yearsC * Beliefs + (1+ yearsC|Id)'
mod.1aa <-lmer(pwi_formula_simple, data= d_3)
mod.2aa <-lmer(ls_formula_simple, data= d_3)

# table
sjPlot::tab_model(mod.1aa,mod.2aa)
```

Here is a predictive graph for years $\times$ beliefs interaction on PWI. Rhe function for producing this graph is in the `funs.R` file.

```{r Bayesian_pwi_predict, cache =TRUE}
graph_predictions(mod.1aa, "Predicted Values of Personal well-being")
```

Here is a predictive graph for the years $\times$ beliefs interaction on life satisfaction.

```{r Bayesian_lifesat_predict, cache =TRUE}
graph_predictions(mod.2aa, "Predicted Values of Life Satisfaction")
```

## Fully saturated model

Next we attempted a model with that is adjusted by "usual suspect" demographic indicator. The inference remains unchanged.

```{r lmer_model_with_full_covariates, cache =TRUE}
library(lme4)
pwi_formula <- 'PWI ~  yearsC * Beliefs +  Age_in_Decades_C + Deprivation_S + Education_S  + Employed + Ethnic_Categories + Male  + Has_Partner  + Political_Conservativism_S + Urban + (1 + yearsC|Id)'
ls_formula <- 'LIFESAT ~  yearsC * Beliefs +  Age_in_Decades_C + Deprivation_S + Education_S  + Employed + Ethnic_Categories + Male  + Has_Partner  + Political_Conservativism_S + Urban + (1 + yearsC|Id)'

mod.1 <-lmer (pwi_formula, data= d_3)
mod.2 <-lmer (ls_formula, data= d_3)
```

Here is the table.
```{r saturated model, cache = TRUE, dependson=d_3}
sjPlot::tab_model(mod.1,mod.2)
```

We compared complex with simple models, and we found the inference does not change. 
```{r}
# identical result
sjPlot::tab_model(mod.1,mod.1aa)
sjPlot::tab_model(mod.2,mod.2aa)
```

Next we checked for multi-collinearity. Multi-collinearity is low. (Note that we centre the "years" variable, had we not done this, mult-collinearity would have been high).

```{r check collinearity, cache =TRUE}
# Low VIFS from 
performance::check_collinearity(mod.1)
performance::check_collinearity(mod.2)
```

```{r cache =TRUE}
g1<-plot(parameters::model_parameters(mod.1aa))+ ggtitle("Personal well-being Coefficients")
g2<-plot(parameters::model_parameters(mod.2aa))+ ggtitle("Life Satisfaction Coefficients")
```

```{r plot_coefficientplots_LMER_FULL, cache = TRUE}
g1/g2
```

@@

```{r run all the models with different ns, cache = TRUE}
mod.1_3 <-lmer (pwi_formula_simple, data= d_4)
mod.2_3 <-lmer (ls_formula_simple, data= d_4)

mod.1_4 <-lmer (pwi_formula_simple, data= d_4)
mod.2_4 <-lmer (ls_formula_simple, data= d_4)

mod.1_5 <-lmer (pwi_formula_simple, data= d_5)
mod.2_5 <-lmer (ls_formula_simple, data= d_5)

mod.1_6 <-lmer (pwi_formula_simple, data= d_6)
mod.2_6 <-lmer (ls_formula_simple, data= d_6)

mod.1_7 <-lmer (pwi_formula_simple, data= d_7)
mod.2_7 <-lmer (ls_formula_simple, data= d_7)

mod.1_8 <-lmer (pwi_formula_simple, data= d_8)
mod.2_8 <-lmer (ls_formula_simple, data= d_8)
```

@@

Next, we modelled the relationship between having a partner and deprivation. We did so to address a reviewer's worry that we might have introduced correlation of between deprivation and having a partner that could spoil inference. We indeed found such a relationship. This is an important potential confound, and another reason to favour the simple longitudinal model that we used.

```{r checkforref model,cache =TRUE}
m<-lmer (NZdep ~ Partner + (1|Id), data= d_3, na.action = na.omit)
tab_model(m)
model_parameters(m)
```

>>>>

```{r mixing_pwi_DAG, cache=TRUE}
plot(mod.1_bDAG, pars ="b_") 
```

```{r mixing_lsDAG, cache=TRUE}
plot(mod.2_bDAG, pars ="b_") 
```

```{r mixing_sd_pwi, cache=TRUE}
plot(mod.1_bDAG, pars ="sd_") #
```

```{r mixing_ls_pwi, cache=TRUE}
plot(mod.2_bDAG, pars ="sd_") # 
```

@@

@@

@@

@@

```{r run all the models with different ns, cache = TRUE}
mod.1_3 <-lmer (pwi_formulaDag1, data= d_4)
mod.2_3 <-lmer (mod.2dag2, data= d_4)

mod.1_4 <-lmer (pwi_formulaDag1, data= d_4)
mod.2_4 <-lmer (mod.2dag2, data= d_4)

mod.1_5 <-lmer (pwi_formulaDag1, data= d_5)
mod.2_5 <-lmer (mod.2dag2, data= d_5)

mod.1_6 <-lmer (pwi_formulaDag1, data= d_6)
mod.2_6 <-lmer (mod.2dag2, data= d_6)

mod.1_7 <-lmer (pwi_formulaDag1, data= d_7)
mod.2_7 <-lmer (mod.2dag2, data= d_7)

mod.1_8 <-lmer (pwi_formulaDag1, data= d_8)
mod.2_8 <-lmer (mod.2dag2, data= d_8)
```

@@
